|

### 2022-07-25 manuscript.Rmd

We firmly believe that an accessible future in the field of data science requires educators to deliberately teach accessibility as part of the curriculum. 
We also acknowledge that what we have presented here is only a small portion of the intersection of visual accessibility and data science. 
One of the co-authors was supported through a Teach Access grant to develop curricular materials on teaching accessibility as part of the data science curriculum. These open-access teaching materials can be accessed at [HIDDEN FOR REVIEW].

>>>>

We firmly believe that an accessible future in the field of data science requires educators to deliberately teach accessibility as part of the curriculum. 
We also acknowledge that what we have presented here is only a small portion of the intersection of visual accessibility and data science. 
The second co-author was supported through a Teach Access grant to develop curricular materials on teaching accessibility as part of the data science curriculum. 
Educators interested in teaching accessibility can follow the organization's work at https://teachaccess.org/. 
The source code of this manuscript can be found on a \href{\repo{}}{GitHub repository}^[The GitHub repository can be found at \url{\repo{}}]
